Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-09-02 ms/ms08_figures.tex
ENH

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/histplot.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/histplot.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
    \end{subfigure}

@@

%\begin{figure}[!ht]
%    \centering
%
%    \begin{subfigure}[]{.49\textwidth}vep.png
%    \textbf{a}
%    \\
%    \includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
%    \end{subfigure}
%
%    \begin{subfigure}[]{.49\textwidth}
%        \textbf{b}
%        \\
%        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
%    \end{subfigure}
%
%    % Fig 9: eQTL gene distance
%    \begin{subfigure}[]{.49\textwidth}
%        \textbf{c}
%        \\
%        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_egene_distance.py/violin.png}
%    \end{subfigure}
%
%    \caption{}
%    %
%\end{figure}

>>>>

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_etissue_y_egene.py/plt.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_egene_y_etissue.py/plt.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{aa}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_etissue_y_egene.py/boxenplot.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{bb}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_egene_y_etissue.py/boxenplot.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
    \end{subfigure}

@@

%\begin{figure}[!ht]
%    \centering
%
%    \begin{subfigure}[]{.49\textwidth}vep.png
%    \textbf{a}
%    \\
%    \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
%    \end{subfigure}
%
%    \begin{subfigure}[]{.49\textwidth}
%        \textbf{b}
%        \\
%        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
%    \end{subfigure}
%
%    % Fig 9: eQTL gene distance
%    \begin{subfigure}[]{.49\textwidth}
%        \textbf{c}
%        \\
%        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_egene_distance.py/violin.png}
%    \end{subfigure}
%
%    \caption{}
%    %
%\end{figure}
